Attract and kill: Spinosad containing spheres to control onion maggot (\textit{Delia antiqua})

### 2020-03-11 manuscript/pest-management-science/main.tex
Updated references with numbering upon request from Pest Management Science.

\documentclass[alpha-refs]{wiley-article}
% \documentclass[blind,num-refs]{wiley-article}

@@

Allium crops worldwide suffer attack from onion maggot (\textit{Delia antiqua} Meigen).  Present in the Americas, Europe and Asia, \textit{Delia antiqua} is well established in most temperate onion growing regions and causes crop losses of up to 100 percent on onions (\textit{Allium cepa} L) if left unmanaged \citep{nault2006performance, nault2006onion}.  Other allium crops including garlic (\textit{Allium sativum} L.), scallions (\textit{Allium fistulosum} L.), and chives (\textit{Allium schoenoprasum} L.) are similarly susceptible \citep{ellis1979factors,ning2017predicting,nault2007ecology}.  Commercial onion production has relied upon intensive management of this pest, but losses continue to occur in places where crop rotation is not used and insecticide-resistant populations are present \citep{martinson1988dispersal, nault2006onion}.

The lifecycle of \textit{Delia antiqua} plays a large role in its severity as an onion pest.  In the northern United States, three generations per year are common \citep{eckenrode1975population, hoepting2004insecticide}. In New York, \textit{D. antiqua} overwinters as a pupa and adults emerge in late April to early May and peak in late May to early June. The next generation begins to emerge in late June to early July and peaks in mid to late July, while the last generation adults begin to emerge in late July to early August and peak in mid to late August \citep{nault2011delaying}. While adults can be captured in fields using sticky cards, the larvae cause devastating damage by feeding on plant roots and onion bulbs \citep{nault2006onion, nault2006performance}. Feeding by \textit{D. antiqua} larvae early in the season can kill seedlings and damaged plants can become more susceptible to infection by pathogen and attack by subsequent generations \citep{eckenrode1986impact,nault2006performance}.  Feeding by \textit{D. antiqua} larvae, even if it does not completely kill the onion can cause sufficient damage to prevent sale of the bulb.

@@

To evaluate the efficacy of attract and kill techniques for reducing \textit{D. antiqua} larval damage, onions killed or damaged by \textit{D. antiqua} larvae were monitored throughout the field seasons of 2007 and 2008. Onion seed of \textit{Allium cepa} L. ’Arsenal’, an early yellow globe variety, was planted in late April with plants subjected to treatments in a randomized controlled block design with six replicates across three field sites.  Six treatment combinations were evaluated (i.e., insecticide-treated plants only [positive control], non-insecticide treated plants with spinosad containing white spheres only, non-insecticide treated plants with spinosad containing white spheres and Delia Lure, non-insecticide treated plants with white sticky cards only, non-insecticide treated plants with white sticky cards and Delia Lure, and non-insecticide treated plants only [negative control]).  Insecticide-treated plants were grown from seeds treated with the Trigard OMC and Pro-Gro fungicide.  This treatment was included in the experiment to be a positive control. Non-insecticide treated plants were grown from fungicide-only treated seeds (thiram [Thiram 42 S {@}188 mg a.i./ 100 g seed] and tebuconazole [Raxil 2.6 F @ 250 mg a.i. / 100 g seed]) and did not receive any attract and kill strategies. Spinosad spheres containing 0.5\% spinosad were deployed with and without attractive Delia Lures (AgBio, Westminster, CO) as an attract and kill solution. White sticky cards with and without attractive Delia Lure were also deployed.

@@

\bibliographystyle{vancouver-authoryear}
\bibliography{om-attraction}

>>>>

\documentclass[num-refs]{wiley-article}
% \documentclass[blind,num-refs]{wiley-article}

@@

Allium crops worldwide suffer attack from onion maggot (\textit{Delia antiqua} Meigen).  Present in the Americas, Europe and Asia, \textit{Delia antiqua} is well established in most temperate onion growing regions and causes crop losses of up to 100 percent on onions (\textit{Allium cepa} L) if left unmanaged \cite{nault2006performance, nault2006onion}.  Other allium crops including garlic (\textit{Allium sativum} L.), scallions (\textit{Allium fistulosum} L.), and chives (\textit{Allium schoenoprasum} L.) are similarly susceptible \citep{ellis1979factors,ning2017predicting,nault2007ecology}.  Commercial onion production has relied upon intensive management of this pest, but losses continue to occur in places where crop rotation is not used and insecticide-resistant populations are present \citep{martinson1988dispersal, nault2006onion}.

The lifecycle of \textit{Delia antiqua} plays a large role in its severity as an onion pest.  In the northern United States, three generations per year are common \cite{eckenrode1975population, hoepting2004insecticide}. In New York, \textit{D. antiqua} overwinters as a pupa and adults emerge in late April to early May and peak in late May to early June. The next generation begins to emerge in late June to early July and peaks in mid to late July, while the last generation adults begin to emerge in late July to early August and peak in mid to late August \citep{nault2011delaying}. While adults can be captured in fields using sticky cards, the larvae cause devastating damage by feeding on plant roots and onion bulbs \citep{nault2006onion, nault2006performance}. Feeding by \textit{D. antiqua} larvae early in the season can kill seedlings and damaged plants can become more susceptible to infection by pathogen and attack by subsequent generations \citep{eckenrode1986impact,nault2006performance}.  Feeding by \textit{D. antiqua} larvae, even if it does not completely kill the onion can cause sufficient damage to prevent sale of the bulb.

@@

To evaluate the efficacy of attract and kill techniques for reducing \textit{D. antiqua} larval damage, onions killed or damaged by \textit{D. antiqua} larvae were monitored throughout the field seasons of 2007 and 2008. Onion seed of \textit{Allium cepa} L. ’Arsenal’, an early yellow globe variety, was planted in late April with plants subjected to treatments in a randomized controlled block design with six replicates across three field sites.  Six treatment combinations were evaluated (i.e., insecticide-treated plants only [positive control], non-insecticide treated plants with spinosad containing white spheres only, non-insecticide treated plants with spinosad containing white spheres and Delia Lure, non-insecticide treated plants with white sticky cards only, non-insecticide treated plants with white sticky cards and Delia Lure, and non-insecticide treated plants only [negative control]).  Insecticide-treated plants were grown from seeds treated with Trigard OMC and fungicide.  This treatment was included in the experiment to be a positive control. Non-insecticide treated plants were grown from fungicide-only treated seeds (thiram [Thiram 42 S {@}188 mg a.i./ 100 g seed] and tebuconazole [Raxil 2.6 F @ 250 mg a.i. / 100 g seed]) and did not receive any attract and kill strategies. Spinosad spheres containing 0.5\% spinosad were deployed with and without attractive Delia Lures (AgBio, Westminster, CO) as an attract and kill solution. White sticky cards with and without attractive Delia Lure were also deployed.

@@

\bibliographystyle{vancouver}
\bibliography{om-attraction}
